Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
improving explanation of bug#24

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with 
differential testing using radamsa on a repository mined from GitHub.
The original test case contains a string concatenation. 
This is a case of validation of RegExp flags. The fuzzer mutate
the file with a regular expression "/v/" between the plus operator and
the variable. The plus operator in this case is used as a flag of the RegExp "+/v/",
but in this case the plus operator is not valid. The behavior expected
is throws an early SyntaxError due to a invalid regular expression flag,
but \hermes Hermes seems not treats the early validation of the regexp flags
as commented by a maintainer.

>>>>

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with 
differential testing using radamsa on a repository mined from GitHub.
The original test case contains a string concatenation. 
This is a case of validation of RegExp flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
but this flag is not valid. The behavior expected is throws an early
SyntaxError due to a invalid regular expression flag,
but \hermes\ seems not treats the early validation of the regexp flags
as commented by a maintainer.
